COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-13 main.tex
Add citation for resonance order and strength

The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
these two quantities is described by equation \ref{eq:tiss}. In the EJ simulation, the eccentricity remains enhanced between the 
MMRs due to the secular forcing by Jupiter. Because the strength of the resonances scales with the initial eccentricity of the planetesimals, 
the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 MMR spikes also grows because the 
strength of a MMR scales as $e^{k}$, where $k$ is the order of the resonance (citation needed).

@@

Most notably, the MMRs appear to have a measurable effect on the local collision rates. This is in contrast to \citet{2000Icar..143...45R}, 
who simulated a similar setup and found no discernible features near the MMRs. We attribute the difference to a more careful treatment of 
timestepping in our simulations. Slightly interior to the 2:1 resonance, the collision rate increases by a factor of roughly 2. In the EJ 
simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. We attribute this to the fact that the strength of a 
second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$. One would therefore expect the 3:1 resonance to 
have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate as a function of semimajor 
axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately indicate where the dust 
generated by collisions will end up in the disk.

>>>>

The MMRs are most clearly visible when viewing the semimajor axis and eccentricity distribution of the planetesimals. This is shown 
in figure \ref{fig:ae}. The top panel corresponds to the CJ simulation and the bottom panel corresponds to EJ. The solid vertical lines 
in this plot represent the nominal locations of the resonances. Near the nominal resonance locations, the a-e distribution of the 
planetesimals exhibits well-defined spikes which curve slightly inward due to conservation of the Jacobi energy. In the EJ simulation, 
the eccentricity distribution of bodies near resonance extends below the initial forced value. This is a reflection of the fact that these 
bodies are undergoing libration, which drives periodic oscillations in both semimajor axis and eccentricity. The coupling between 
these two quantities is described by equation \ref{eq:tiss}. In the EJ simulation, the eccentricity remains enhanced between the 
MMRs due to the secular forcing by Jupiter. Because the strength of the resonances scales with the initial eccentricity of the planetesimals, 
the eccentricity spikes are larger in the EJ simulation. Additionally, the relative size of the 3:1 and 5:3 MMR spikes also grows because the 
strength of a MMR scales as $e^{q}$, where $q$ is the order of the resonance \citep{1994PhyD...77..289M}.

@@

Most notably, the MMRs appear to have a measurable effect on the local collision rates. This is in contrast to \citet{2000Icar..143...45R}, 
who simulated a similar setup and found no discernible features near the MMRs. We attribute the difference to a more careful treatment of 
timestepping in our simulations. Slightly interior to the 2:1 resonance, the collision rate increases by a factor of roughly 2. In the EJ 
simulation, there is a significant deficiency in the number of collisions near the 3:1 MMR. We attribute this to the fact that the strength of a 
second order MMR scales as $e^{2}$, while a first order MMR scales linearly with $e$ \citep{1994PhyD...77..289M}. One would therefore 
expect the 3:1 resonance to have more of an influence on the collision rate in a secularly perturbed disk. Although viewing the collision rate 
as a function of semimajor axis demonstrates a clear connection between the resonances and the collision rate, this does not immediately 
indicate where the dust generated by collisions will end up in the disk.
